---
format: html
title: "R Knowledge & Trivia Quiz"
author: "Ontario Data User Group"
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/templates)'
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

Welcome! This is a short and fun survey/quiz to test your knowledge of the R language and learn a bit about your experience. 

Note: The data recorded is publicly available. The source for this survey is
available at [https://github.com/JasonLocklin/survey-demo](https://github.com/JasonLocklin/survey-demo)

---

## Your R Experience

Let's start with a few questions about your journey with R.

```{r}
# Question 1: Experience Level
sd_question(
  type = 'mc',
  id = 'r_experience_years',
  label = 'How long have you been using R?',
  option = c(
    'Just getting started (less than a year)',
    'I know my way around (1-3 years)',
    'We go way back (3-5 years)',
    "I'm a seasoned veteran (more than 5 years)",
    "Hadley Wickham calls me on my birthday"
  )
)

# Question 2: Favorite Packages
sd_question(
  type = 'mc_multiple_buttons',
  id = 'r_packages',
  label = 'Which of these Tidyverse (and related) packages do you use regularly? (Select all that apply)',
  option = c(
    'dplyr for data manipulation',
    'ggplot2 for visualizations',
    'quarto or rmarkdown for documents',
    'shiny for web apps',
    'radlibs for generating madlibs text content'
  )
)

# Question 3: Comfort with Functions
sd_question(
  type = 'slider',
  id = 'r_function_comfort',
  label = 'On a scale of 1 to 10, how comfortable are you with writing your own functions in R?',
  option = c(
    "function() print('Very Comfortable')"     = "very_comfortable",
    "Somewhat Comfortable" = "somewhat_comfortable", 
    "Somewhat Uncomfortable" = "somewhat_uncomfortable",
    "Very Uncomfortable"   = "very_uncomfortable"
    )
)

#favorite R function
sd_question(
  type  = "text",
  id    = "function",
  label = "What's your favorite R function?"
)
```






```{r}
sd_next(next_page = 'page2')
```

:::

::: {.sd_page id=page2}
---

## R Trivia!

Time for some fun trivia. Let's see how well you know R's history and quirks.

```{r}
# Question 4: R development
sd_question(
  type  = 'date',
  id    = 'published',
  label = "When was the 1.0 release of R published?"
)

# Question: Language dev
sd_question(
  type = 'mc',
  id = 'r_language_influence',
  label = 'R started out as a project to re-write the S language for running on what type of computer?',
  option = c('iPhones', '386 PC', 'Commodore 64', 'Chat GPT', 'Nintendo')
)

# Question: R release names
sd_question(
  type   = 'mc_buttons',
  id     = 'release_names',
  label  = "True or false: R Releases are named after Peanuts comic strips?",
  option = c(
    "True"      = "1",
    "False"     = "0"
  )
)

sd_next()
```


:::

::: {.sd_page id=end}

## End

Thank you for taking the survey, back to the presentation!

```{r}



sd_close()
```

:::
